\documentclass{resume}
\usepackage[left=0.5in, top=0.5in, right=0.5in, bottom=0.5in]{geometry}

\name{Jay Nakum}

\about{
    Rajkot, Gujarat, India \\
    \href{mailto:nakumjay2003+work@gmail.com}{nakumjay2003+work@gmail.com} \\
    +91 94092 59646
}

\about{
    \href{https://jaynakum.github.io}{jaynakum.github.io} \\
    \href{https://linkedin.com/in/JayNakum}{linkedin.com/in/JayNakum} \\  
    \href{https://github.com/JayNakum}{github.com/JayNakum}
}

\begin{document}

\begin{rSection}{Experience}
\vspace{-1em}
    \item \textbf{CSE Summer Intern (Hybrid)}
    \hfill May 2023 - June 2023
    \\ eInfochips (An Arrow Company)
    \hfill Ahmedabad, Gujarat, India
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Worked as a team leader.
        \item Our team developed a full e-commerce website from scratch.
        \item We worked on 3 research based tasks.
        \item The important learnings were leadership skills, teamwork, communication.
        \\ Got a great experience of how to work in industry.
    \end{itemize}
    
    \item \textbf{Flutter Intern (Remote)}
    \hfill Jun 2022 - Sept 2022
    \\ vigIT Solutions
    \hfill Jaipur, Rajasthan, India
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Worked in agile software development model.
        \item Helped the team develop and publish 2 flutter apps.
        \item \href{https://drive.google.com/file/d/1yF5baJ-uIWpwAHL0Sd-CwycYHjbyFumW/view?usp=sharing}{Completion Letter}
    \end{itemize}
\end{rSection}

\begin{rSection}{Projects}
\vspace{-1em}
    \item \textbf{Ray Tracer} | {C++, CUDA}
    \hfill \href{https://github.com/JayNakum/LearningRayTracing}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Learning ray tracing and gpu programming in CUDA.
        \item Implemented different basic materials such as diffuse, metals and dielectrics.
    \end{itemize}

    \item \textbf{Happy Face} | {C++, OpenGL}
    \hfill \href{https://github.com/JayNakum/HappyFace}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Developing a scene based opengl renderer, merging all the bits and pieces into one project.
        \item Implemented shaders, textures, transformations and coordinate systems, lighting, model loading.
    \end{itemize}

    \item \textbf{BitNCrypt} (University Project) | {C++}
    \hfill \href{https://github.com/JayNakum/BitNCrypt}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Designed an algorithm based on the similar concepts of hashing.
        \item It can be used to generate and manage passwords.
    \end{itemize}

    \item \textbf{Out For Delivery} | {C++, OpenGL}
    \hfill \href{https://github.com/JayNakum/OutForDelivery}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Implemented all the basic knowledge of opengl and 2D graphics.
        \item A pocket tanks like game where you shoot delivery packages.
    \end{itemize}

    \item \textbf{CPU Scheduling Simulator} (University Project) | {Python, Flutter, Firebase}
    \hfill \href{https://github.com/JayNakum/OperatingSystemsProject}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Developed a simulator for cpu process scheduling algorithms.
        \item Implemented algorithms such as FCFS, SJF, SRTF and RR.
    \end{itemize}

    \item \textbf{LiViD} (University Project) | {Flutter, Firebase}
    \hfill \href{https://github.com/JayNakum/LiViD}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Developed a live streaming app using Agora SDK.
        \item This project won 2nd place in SSIP competition for Saurashtra Kutch Region, Gujarat.
    \end{itemize}

    \item \textbf{eXPe} | {Flutter, SQLite}
    \hfill \href{https://github.com/JayNakum/eXPe}{GitHub}
    \begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Published a simple expense tracker on \href{https://play.google.com/store/apps/details?id=io.github.jaynakum.expe&pcampaignid=pcampaignidMKT-Other-global-all-co-prtnr-py-PartBadge-Mar2515-1}{google playstore}.
    \end{itemize}
\end{rSection}

\newpage

\begin{rSection}{Education}
\vspace{-1em}
    \item \textbf{Pandit Deendayal Energy University (School of Technology)}
    \hfill Gandhinagar, Gujarat
    \\ Bachelor of Technology - Computer Science and Engineering - 9.85 CGPA
    \hfill {Aug 2021 - Present}

    \item \textbf{A. V. Parekh Technical Institute (Gujarat Technological University)}
    \hfill Rajkot, Gujarat
    \\ Diploma - Computer Engineering - 9.74 CGPA
    \hfill {Aug 2018 - Jun 2021}

    \item \textbf{Kendriya Vidyalaya (Central Board of Secondary Education)}
    \hfill Rajkot, Gujarat
    \\ Class 1 to 10 - 85.6\% 
    \hfill {Apr 2008 - Mar 2018}
\end{rSection}

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1em}} l }
    Tech
    & C++, OpenGL, GLSL, CUDA, Python, Flutter, Firebase, SQL
    \\ Developer Tools 
    & Git, GitHub, Visual Studio, VS Code, Android Studio
    \\ Operating Systems 
    & Linux (Manjaro / Arch), Windows, Android
    \\ Fields 
    & Computer Graphics, GPU Architectures and Programming, Algorithms, Game Engines
    \\ Soft Skills 
    & Problem Solving, Time Management, Teamwork, Leadership, Accountability, \\
    & Explaining and Teaching, Communication
\end{tabular}
\end{rSection}

\begin{rSection}{Awards and Certifications}
\begin{itemize}
    \item \href{https://internalapp.nptel.ac.in/noc/Ecertificate/?q=NPTEL23CS61S3357054004192946}{NPTEL: GPU Architectures and Programming}
    \item \href{https://courses.edx.org/certificates/3e47add62a6b45269149bf91b91f1399}{EDX: UCSD CSE167x: Computer Graphics}
    \item \href{https://www.udemy.com/certificate/UC-2fce7723-1cc7-403d-a54b-09dbd5cd495e/}{UDEMY: Flutter and Dart - The Complete Guide}
    \item \href{https://drive.google.com/file/d/1S-b58wIceYXIlX24bubJy8Z2aT2lQV2d/view?usp=sharing}{TRINITY, LONDON: Grade 4 - Theory of Music}
\end{itemize}
\end{rSection}

\begin{rSection}{Roles and Responsibilities}
\begin{itemize}
    \item {Technical Head} | {Computer Society of India, Student Chapter PDEU}
    \item {Application Development Lead} | {Google Developer Students Club, PDEU}
    \item {General Secretary} | {The Hackers Meetup, Student Chapter PDEU}
    \item {Application Development Head} | {Encode, Students Club PDEU}
\end{itemize}
\end{rSection}

\begin{rSection}{Languages}
\begin{itemize}
    \item English (Professional proficiency)
    \item Hindi (Professional proficiency)
    \item Gujarati (Native proficiency)
\end{itemize}
\end{rSection}

\begin{rSection}{Hobbies and Interests}
Guitar Playing, Music Theory, Singing, Music Composing, Staff Notations, Orchestration, Harmonizing, Voicing,
\\ Digital Image Processing, Compiler Designing, Cryptography, Theory of Computation, Mathematics, Learning
\end{rSection}

\end{document}
