\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jay Nakum} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{Rajkot, Gujarat, India \\ +91 94092 59646 \\
% \href{mailto:nakum.jay.m@gmail.com}{nakum.jay.m@gmail.com}} 
\href{mailto:contact.jaynakum@gmail.com}{contact.jaynakum@gmail.com}}
%\href{mailto:jay.nce20@sot.pdpu.ac.in}{jay.nce20@sot.pdpu.ac.in}}
\address{Portfolio Website: \href{https://jaynakum.github.io/}{jaynakum.github.io} \\ LinkedIn: \href{https://linkedin.com/in/JayNakum}{JayNakum} \\  GitHub: \href{https://github.com/JayNakum}{JayNakum}}

\begin{document}

%------------------------
% Use this more detailed section if you have Relevant work experience
% keep your resume to 1 page, if you need to remove a project to display relevant experience
% that is okay
% ----------------------------
% \begin{rSection}{EXPERIENCE}

% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}
 
% \textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
% Company Name \hfill \textit{San Francisco, CA}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved X\% growth for XYZ using A, B, and C skills.
%      \item Led XYZ which led to X\% of improvement in ABC
%     \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}

% \end{rSection} 

% \begin{rSection}{Work History}
% \vspace{-1.25em}
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \item \textbf{Job Title} {Company} \hfill Month Year - Month Year
% \end{rSection} 

%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Vector Engine} | {OpenGL, C++} \hfill \href{https://github.com/JayNakum/VectorEngine}{Currently Working}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Developing a 3D game engine.
    \item Trying to develop an easy to use engine for 3D rendering.
 \end{itemize}

\item \textbf{IIC PDEU} | {Flutter, REST API} \hfill {Currently Working}
\begin{itemize}
    \itemsep -3pt {} 
    \item Currently working on an application for Innovation and Incubation Centre \href{https://iic.pdpu.ac.in/en}{(IIC)} ,PDEU.
    \item The applications is for managing startups and mentors through an app.
 \end{itemize}

\item \textbf{Out For Delivery} | {C++, OpenGL} \hfill \href{https://jaynakum.itch.io/out-for-delivery}{Itch.io}
\begin{itemize}
    \itemsep -3pt {} 
    \item Developed a 2D game using opengl.
    \item Implemented a lot of skills I gained during the learning process.
 \end{itemize}

\item \textbf{CPU Scheduling Simulator} | {Python, Dart, Flutter, Firebase, Google Colab, Jupyter Notebook} \hfill \href{https://github.com/JayNakum/OperatingSystemsProject}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
    \item Developed a simulator for process scheduling in Flutter.
    \item Implemented FCFS, SJF, SRTF and RR algorithms in Python.
    \item Retrived user input from firebase for scheduling.
 \end{itemize}
\item \textbf{Wave} | {Java} \hfill \href{https://github.com/JayNakum/Wave}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
    \item Developed a single player game.
    \item Implemented some calculations for an enemy to follow the player automatically.
 \end{itemize}
\item \textbf{Portfolio} | {Github Pages, HTML, CSS, JavaScript} \hfill \href{https://github.com/JayNakum/JayNakum.github.io}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
    \item Created a portfolio website hosted via github pages.
 \end{itemize}
\item \textbf{LiViD} | {Dart, Flutter, Firebase, Agora} \hfill \href{https://github.com/JayNakum/LiViD}{GitHub}
\begin{itemize}
    \itemsep -3pt {} 
     \item Created a live streaming app.
    \item Implemented agora SDK for live streaming.
 \end{itemize}
\item \textbf{eXPe} | {Dart, Flutter, SQLite} \hfill \href{https://github.com/JayNakum/eXPe}{GitHub}, \href{https://play.google.com/store/apps/details?id=io.github.jaynakum.expe&pcampaignid=pcampaignidMKT-Other-global-all-co-prtnr-py-PartBadge-Mar2515-1}{Playstore}
\begin{itemize}
    \itemsep -3pt {} 
     \item Published a simple expense tracker app.
 \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Tech 
& C++, OpenGL, Flutter, Dart, \\
& REST API, Firebase, SQLite, \\ 
& Java, Python, C, SQL, HTML, CSS, \\
& Android, Graphics Programming, LibGDX \\

Developer Tools 
& Git, GitHub, VS Code, Visual Studio, \\ 
& Eclipse, Google Colaboratory, Jupyter Notebook, Android Studio, Canva \\

Operating Systems 
& Linux (Manjaro / Arch), Windows, Android \\

Fields 
& Graphics Programming, Flutter Development,\\
& Data Structures and Algorithms, \\ & Research, Deep Learning, Machine Learning\\
Soft Skills 
& Problem Solving, Time Management, Teamwork, Leadership,\\
& Accountability, Communication
\\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf School of Technology (Pandit Deendayal Energy University)} \hfill {Gandhinagar, Gujarat}\\
Bachelor of Technology - Compter Science and Engineering - 9.8 CGPA \hfill {Aug 2021 - Present}\\
\\
{\bf Shree Amrutlal Veerpal Parekh Technical Institute (Gujarat Technological University)} \hfill {Rajkot, Gujarat}\\
Diploma - Computer Engineering - 9.74 CGPA \hfill {Aug 2018 - Jun 2021}\\
\\
{\bf Kendriya Vidyalaya (Central Board of Secondary Education)} \hfill {Rajkot, Gujarat}\\
X Grade - 85.6\% \hfill {Apr 2008 - Mar 2018}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
\begin{itemize}
    \item   \href{https://www.udemy.com/certificate/UC-2fce7723-1cc7-403d-a54b-09dbd5cd495e/}{Flutter and Dart - The Complete Guide - UDEMY}
    \item   \href{https://jaynakum.github.io/assets/Achievements/SSIP.jpg}{SSIP Project Competition}
    \item   \href{https://jaynakum.github.io/assets/Achievements/JPMC.jpg}{JPMorgan SE Virtual Program}
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\begin{rSection}{Interests} 
\begin{itemize}
    Graphics Programming, Game/Graphics Engine Development, Flutter, Game AI, Game Development, Artificial Intelligence, Machine Learning, Deep Learning, Software Development, Problem Solving
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\begin{rSection}{Languages Known} 
\begin{itemize}
    \item English (Full professional proficiency)
    \item Hindi (Full professional proficiency)
    \item Gujarati (Native proficiency)
    \item Japanese (Elementary proficiency)
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Hobbies} 
\begin{itemize}
    \item Playing Guitar
\end{itemize}
\end{rSection}

\end{document}
